The Holy Hand Grenade of Antioch

### 2020-02-23 draft-camelot-holy-grenade.tex
fix: drop deprecated note
fix: fix improper mncite usage

The \textit{Cave of Caerbannog} has been well-established in the mythology
of Camelot (as recounted by Monty Python) as the lair of the
Legendary Black Beast of Arrrghhh, more commonly known today as the
\textbf{Killer Rabbit of Caerbannog} \mncite{killer_rabbit_caerbannog}.
It is the encounter between the Killer Rabbit of Caerbannog and the
Knights of the Round Table, armed with the Holy Hand Grenade of
Antioch (see the \mncite{holy_hand_grenade,following section}), that we
recount here through monospace font and multiple spaces.

\subsection{The Killer Rabbit of Caerbannog}
\label{killer_rabbit_caerbannog}
% TODO: this label ain't behaving -- why?

@@

The \textbf{Killer Rabbit of Caerbannog}, that most formidable foe of
the Knights and of all that is holy or carrot-like, has been
depicted diversely in lay and in song. We venture to say,
\textit{contra} the claim made in \mncite{RFC8140,4.1 of: Ze Vompyre},
that the Killer Rabbit of Caerbannog truly is the most afeared
of all the creatures. Short of sanctified ordnance such as
\mncite{holy_hand_grenade,format=title}, there are few remedies
known against its awful lapine powers.

@@

\mncite{killer-bunny,The following depiction} of the fearsome beast
has been sourced from
\url{http://camelot.gov.example/avatars/rabbit[Rabbit-SCII]},
\mncite{killer-source,accompanied}
by C code that was used in this accurate depiction of the
Killer Rabbit:

>>>>

The \textit{Cave of Caerbannog} has been well-established in the mythology
of Camelot (as recounted by Monty Python) as the lair of the
Legendary Black Beast of Arrrghhh, more commonly known today as the
\textbf{Killer Rabbit of Caerbannog} \mncite{killer_rabbit_caerbannog}.
It is the encounter between the Killer Rabbit of Caerbannog and the
Knights of the Round Table, armed with the Holy Hand Grenade of
Antioch (see the \mncite[following section]{holy_hand_grenade}), that we
recount here through monospace font and multiple spaces.

\subsection{The Killer Rabbit of Caerbannog}
\label{killer_rabbit_caerbannog}

@@

The \textbf{Killer Rabbit of Caerbannog}, that most formidable foe of
the Knights and of all that is holy or carrot-like, has been
depicted diversely in lay and in song. We venture to say,
\textit{contra} the claim made in \mncite{RFC8140}[4.1 of: Ze Vompyre],
that the Killer Rabbit of Caerbannog truly is the most afeared
of all the creatures. Short of sanctified ordnance such as
\mncite{holy_hand_grenade}[format=title], there are few remedies
known against its awful lapine powers.

@@

\mncite[The following depiction]{killer-bunny} of the fearsome beast
has been sourced from
\url{http://camelot.gov.example/avatars/rabbit[Rabbit-SCII]},
\mncite[accompanied]{killer-source}
by C code that was used in this accurate depiction of the
Killer Rabbit:
